\textbf{Teaching a machine to generate an artificial universe}

### 2020-09-23 paper.tex
KL trials for 'unseen' redshifts

\setcounter{tocdepth}{2}
\begingroup
\let\clearpage\relax
\tableofcontents
\endgroup
\newpage

@@

In the ACGAN framework each generated sample has a corresponding label $c \sim p_c$ and noise vector $\mathbf{z} \sim p_z$ 
which make the generator create a sample $G(c, \mathbf{z})$. The discriminator $D$ gives probability distributions $P(S|X)$ 
and $P(C|X) = D(X)$ over the sources of the samples $S$ and class labels $C$. The objective function is made of two 
independent parts; the likelihood of a correct source $L_S$ and the log-likelihood of the correct class $L_C$

\begin{eqnarray}
    L_S &=& \EE [\log P(S = \textup{real} | X_{real})] \nonumber \\
        &+& \EE [\log P(S = \textup{fake} | X_{fake})] \\ 
        & & \nonumber \\ 
    L_C &=& \EE [\log P(C = c | X_{real})] \nonumber \\
        &+& \EE [\log P(C = c | X_{fake})]
\end{eqnarray}

@@

@@

\begin{figure}[hbt!]
\includegraphics[width=\columnwidth]{figures/diagrams/mill_catalog_comparison.png}
\centering
\caption[]{A comparative diagram of Millennium simulation data against galaxy survey data\protect\footnotemark.}
\label{fig:gal_catalogs}
\end{figure}
\footnotetext{Image from \url{wwmpa.mpa-garching.mpg.de/millennium}.}

@@

The galaxy catalogs containing physical properties of galaxies in the Millennium simulation were derived with the 
Semi-Analytic Galaxy Evolution (SAGE) codebase by Croton et al. 2016~\cite{Croton2016} that improves on the earlier 
model of Croton et al. 2006~\cite{Croton2006}. The SAGE catalogs were sourced from the Theoretical Astrophysical 
Observatory (TAO)~\cite{TAO}. SAGE modelling adds baryonic processes into N-body simulations of halos after the 
simulations have been run. The baryonic particle properties are from information in the simulation run such as mass, 
size, spin and their merger history. SAGE models account for different mechanisms that affect the evolutions of 
galaxies and therefore the evolution of cosmological structure. The N-body particle positions of the Millennium-SAGE 
data were taken at snapshots at discrete redshifts $z=\{0.00, 1.07, 2.07, 3.06, 4.18, 5.28\}$ to give the training 
data for the ACGAN.

@@

@@

where $a$ is a free parameter that depends on the sparsity of the histogram densities. This is applied element-wise across 
the training data for all redshifts $z$. The value of $a=1.25$ was found to be optimal for the 
$200 \:  \: h^{-1} \,\textup{Mpc}$ histograms at all redshifts $z$. This parameter remains fixed during training. The value 
of $a$ controls the median pixel density of the scaled image. Figure \ref{fig:scaling} shows the difference between scaled 
images $s(\mathbf{x})$ and the original images $\mathbf{x}$. The inverse transformation $s^{-1}(\mathbf{x})$ can be applied 
to obtain the original image. 
% A logarithmic scaling was used originally, but this did not provide good results with the GAN architecture that used 
% the hyperbolic tangent ($\tanh$) activation because the logarithm of a negative number is undefined. The models using 
% $\tanh$ activations achieved much better results than models without these activations.

@@

The ACGAN implementation was limited by the GPU memory capacity - the parameters and architectures together with the 
sample batch sizes meant that the GPU was easily saturated. Deeper models with more convolutional units were implemented 
but these tended to stall the GPU. A training loop for $10^5$ epochs for the $200 \: h^{-1} \: \textup{Mpc}$ cubes 
formatted to $32 \times 32 \times 32$ pixel histograms took approximately 144 hours on an NVIDIA Tesla V100 GPU with 
32GB capacity.

@@

where a discrete set of points between points $q_1$ and $q_2$ are passed to the generator model to create samples~with.

@@

\section{Statistics and diagnostics}\label{sec:stats_and_diags}
% WHAT ARE THESE MEASURES FOR? WHY ARE THEY IMPORTANT TO THE EXPERIMENT ? 
% WHAT DO THE STATS CONSIST OF IN MAKING? WHAT DO THEY SHOW?

@@

@@

\subsection{Generated images}
% show generated images at various redshifts, compare with training data
Figures~\ref{fig:t_z_imgs} and ~\ref{fig:g_z_imgs} show separate collections of simulated cosmic web and GAN-generated 
cosmic web for each class of redshift in the Millennium-SAGE training data. Across each value of redshift the ACGAN 
demonstrates its ability to evaluate each point in the latent space to a strong representation

@@

\begin{figure*}[hbt!]
\includegraphics[width=17cm]{figures/cubes/acgan3d_g_fig.png}
\centering
\caption{A collection of training data cubes extracted from the Millennium-SAGE catalogs.Each row corresponds to the 
         redshift value given above each cube. The scaling $s(\mathbf{x})$ is applied to each cube $\mathbf{x}$.}
\label{fig:t_z_imgs}
\end{figure*}

\begin{figure*}[hbt!]
\includegraphics[width=16cm]{figures/cubes/acgan2d_t_fig.png}
\centering
\caption{A collection of 2D-projections of training data cubes extracted from the Millennium-SAGE catalogs. Each row 
         corresponds to the redshift value given above each cube. The scaling $s(\mathbf{x})$ is applied to each cube 
         $\mathbf{x}$.}
\label{fig:t_z_imgs}
\end{figure*}

\begin{figure*}[hbt!]
\includegraphics[width=17cm]{figures/cubes/acgan2d_g_fig.png}
\centering
\caption{A collection of 2D-projections of generated data cubes extracted from the Millennium-SAGE catalogs. Each row 
         corresponds to the redshift value given above each cube. The scaling $s(\mathbf{x})$ is applied to each cube 
         $\mathbf{x}$.}
\label{fig:t_z_imgs}
\end{figure*}

@@

\begin{figure}[!ht]%[hbt!]
\includegraphics[width=\columnwidth]{figures/cubes/acgan3d_interp.png}
\centering
\caption{A collection of images generated with an array of redshift values for a single latent-space point.}
\label{fig:kernel_fig}
\end{figure}

@@

@@

\begin{figure}[!ht]%[hbt!]
\includegraphics[width=\columnwidth]{figures/graphs/metrics.png}
\centering
\caption{The loss and accuracy curves for the training of the ACGAN.}
\label{fig:2dgan_losscurve}
\end{figure}

@@

\begin{figure*}[hbt!]
\includegraphics[width=17cm]{figures/graphs/kl_trials_all.png}
\centering
\caption{Histograms showing the $D_{KL}$ values for distribution-comparisons between training $t$, generated $g$ and 
         uniform $u$ cube samples. This graph shows the results for downsampling kernel values $k \in\{1, 2, 4\}$.}
\label{fig:t_z_imgs}
\end{figure*}

@@

\begin{table*}[t]
  \centering
  \begin{tabular}{ccccccc}
    \hline\hline
    & $(t||g)$  $(g||t)$ & $(t||u)$ $(u||t)$ & $(g||u)$ $(u||g)$ & $(t||t)$  $(t||t)$ & $(g||g)$  $(g||g)$ & $(u||u)$  $(u||u)$\\ [1ex]
    \hline\hline
    $k=1$ & 0.358 0.344 &  0.619 0.531 & 0.804 0.722 & 0.195 0.195 & 0.196 0.196 & 0.203 0.202  \\ 
    % \hline
    $k=2$ & 0.322 0.309 & 13.879 1.517 & 13.904 1.628 & 0.199 0.199 & 0.202 0.202 & 0.355 0.370 \\
    % \hline
    $k=4$ & 0.309 0.292 & 38.687 2.318 & 38.953 2.438 & 0.196 0.195 & 0.197 0.197 & 0.178 0.180 \\ [1ex]
    \hline\hline
  \end{tabular}
  \caption{Results from the $D_{KL}$ trials averaged over redshift $z$ for each kernel size $k$ for each distribution comparison.}
  \label{tab:1}
\end{table*}

% \begin{table}[h!]
% \centering
% \begin{tabularx}
% {\columnwidth}{@{}l *5{>{\centering\arraybackslash}X}@{}}%{||c c c c c c||} 
%  \hline
%   $(t||g)$  $(g||t)$ & $(t||g)$  $(g||t)$ & $(t||g)$  $(g||t)$ 
%   $(t||g)$  $(g||t)$ & $(t||g)$  $(g||t)$ & $(t||g)$  $(g||t)$\\ [0.5ex]
%     % $D_{KL}(t||g)$  $D_{KL}(g||t)$ & $D_{KL}(t||g)$  $D_{KL}(g||t)$ & $D_{KL}(t||g)$  $D_{KL}(g||t)$ 
% %   $D_{KL}(t||g)$  $D_{KL}(g||t)$ & $D_{KL}(t||g)$  $D_{KL}(g||t)$ & $D_{KL}(t||g)$  $D_{KL}(g||t)$
%  \hline\hline
%  0.358 0.344 &  0.619 0.531 & 0.804 0.722 & 0.195 0.195 & 0.196 0.196 & 0.203 0.202  \\ 
%  0.322 0.309 & 13.879 1.517 & 13.904 1.628 & 0.199 0.199 & 0.202 0.202 & 0.355 0.370 \\
%  0.309 0.292 & 38.687 2.318 & 38.953 2.438 & 0.196 0.195 & 0.197 0.197 & 0.178 0.180 \\ [1ex]
% \hline
% \end{tabularx}
% \caption{Values of critical hyper-parameters used in the ACGAN implementation.}
% \label{table:acgan_params}
% \end{table}

% do the same as before (in thesis) but average over classes?

% This section presents the results of the procedure for the repeated ensemble KL divergence testing. transformed into 
% probability distributions over the pixel density. This comparison is repeated over 100 iterations

% \subsubsection{2D-GAN implementation}
% Figure~\ref{fig:2dgan_kltrials} shows the results of the $D_{KL}$ tests for the 2D-GAN implementation with the $D_{KL}$
% values on each plot of the distribution comparisons. There is a consistent broadening of the histograms along the columns
% of increasing kernel size. This shows the random effect, or dispersion, on the $D_{KL}$ value from repeated tests to on 
% separate ensembles of histograms. This is caused by the loss of information due to the down-sampling of larger areas which
% causes more variance in a given value of pixel density because of the averaging over the original pixels. This is predicted
% by the central-limit theorem. In this discussion a `mutual comparison' refers to the KL divergence $D_{KL}$ between two 
% different ensembles from the same distribution of $t$, $g$ or $u$. The mutual $D_{KL}$ comparisons that show the broadening
% the most are the generated-generated and uniform-uniform comparisons which together have increasing variance and separation
% with kernel size. This shows that in both cases the distributions are composed very differently to the uniform distributions.
% The means of the mutual distributions stay the same except for the uniform-uniform comparison. This is because the median
% for the bin separations in the component-histograms was given by the median of the training data which has a lower mean 
% pixel density than the uniform histogram data. 
% % make pixel dists to show different medians?

% % The smaller value of the generated-generated $D_KL$ average comparison with respect to the other mutual comparisons 
% shows the tendency of generative adversarial networks to represent a few modes in the latent space most. This was 
% affirmed by both implementations tending to mode collapse many epochs after converging. THIS WAS TRUE FOR 3D only 
% I think

% The separate kernels cause averaging over different sized areas in the 2D case (volumes in the 3D case). By 
% construction the histograms are already sampling a volume at a fixed resolution for every distribution and so the kernel
% sizes give the same volume at different levels of resolution. A histogram from any distribution with each kernel 
% down-sampling will exhibit different scales of structure from the original unsampled histogram and this is shown in Figure~\ref{fig:kernel_fig}. The ensembles drawn from each distribution are necessary to measure the difference in the 
% structure from the distributions that is not inherent in the individual variance of the images themselves. The latter 
% difference does not concern the distributions of the samples and is less important for the test of the generator capability.

>>>>

% \setcounter{tocdepth}{2}
% \begingroup
% \let\clearpage\relax
% \tableofcontents
% \endgroup
% \newpage

@@

In the ACGAN framework each sample $\mathbf{x}$ (generated or not) has a corresponding label $c_)\mathbf{x} \sim p_c$ and noise vector $\mathbf{z} \sim p_\mathbf{z}$ 
which make the generator create a sample $G(c_\mathbf{x}, \mathbf{z})$ where $G(c_\mathbf{x}, \mathbf{z}) \in X_\textup{fake}$.
The discriminator $D$ gives probability distributions $P(S|X)$ and $P(C|X) = D(X)$ over the sources of the samples $S \in \{X_\textup{real}, X_\textup{fake}\}$ and class labels $C$. The objective function is made of two independent parts; the 
likelihood of a correct source $L_S$ and the log-likelihood of the correct class $L_C$

\begin{eqnarray}
    % L_S &=& \EE [\log P(S = \textup{real} | X_{real})] \nonumber \\
    %     &+& \EE [\log P(S = \textup{fake} | X_{fake})] \\ 
    %     & & \nonumber \\ 
    % L_C &=& \EE [\log P(C = c | X_{real})] \nonumber \\
    %     &+& \EE [\log P(C = c | X_{fake})]
    L_S &=& \EE [\log P(\mathbf{x} \sim p_{\textup{data}} | \mathbf{x} \sim X_{real})] \nonumber \\
        &+& \EE [\log P(\mathbf{x} \sim p_{\textup{model}} | \mathbf{x} \sim X_{fake})] \\ 
        & & \nonumber \\ 
    L_C &=& \EE [\log P(c_\mathbf{x} = c \, | \mathbf{x} \sim X_{real})] \nonumber \\
        &+& \EE [\log P(c_\mathbf{x} = c \, | \mathbf{x} \sim X_{fake})]
\end{eqnarray}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[hbt!]
\includegraphics[width=\columnwidth]{figures/diagrams/mill_catalog_comparison.png}
\centering
\caption[]{A comparative diagram of Millennium simulation data against galaxy survey data\protect\footnotemark.}
\label{fig:gal_catalogs}
\end{figure}
\footnotetext{Image from \url{wwmpa.mpa-garching.mpg.de/millennium}.}

@@

% \begin{figure}[hbt!]
% \includegraphics[width=\columnwidth]{figures/diagrams/mill_catalog_comparison.png}
% \centering
% \caption[]{A comparative diagram of Millennium simulation data against galaxy survey data\protect\footnotemark.}
% \label{fig:gal_catalogs}
% \end{figure}
% \footnotetext{Image from \url{wwmpa.mpa-garching.mpg.de/millennium}.}

@@

The galaxy catalogs containing physical properties of galaxies in the Millennium simulation were derived with the 
Semi-Analytic Galaxy Evolution (SAGE) codebase by Croton et al. 2016~\cite{Croton2016} that improves on the earlier 
model of Croton et al. 2006~\cite{Croton2006}. The SAGE catalogs were sourced from the Theoretical Astrophysical 
Observatory (TAO)~\cite{TAO}. SAGE modelling adds baryonic processes into N-body simulations of halos after the 
simulations have been run. The baryonic particle properties are from information in the simulation run such as mass, 
size, spin and their merger history. SAGE models account for different mechanisms that affect the evolutions of 
galaxies and therefore the evolution of cosmological structure. The N-body particle positions of the Millennium-SAGE 
data were taken from snapshots at discrete redshifts $z=\{0.00, 1.07, 2.07, 3.06, 4.18, 5.28\}$ to give the training 
data for the ACGAN.

@@

% \begin{figure}
% \includegraphics[width=\columnwidth]{figures/diagrams/scale_fig.png}% scaling2.png
% \centering
% \caption{The application of the scaling $s$ to a 3D-histogram training sample. The cube on the left shows an 
% image $\mathbf{x}$ and on the right is a scaled image $s(\mathbf{x})$.}
% \label{fig:scaling}
% \end{figure}

@@

where $a$ is a free parameter that depends on the sparsity of the histogram densities. This is applied element-wise across 
the training data for all redshifts $z$. The value of $a=1.25$ was found to be optimal for the 
$200 \:  \: h^{-1} \,\textup{Mpc}$ histograms at all redshifts $z$. This parameter remains fixed during training. The value 
of $a$ controls the median pixel density of the scaled image. Figure \ref{fig:scaling} shows the difference between scaled 
images $s(\mathbf{x})$ and the original images $\mathbf{x}$. The inverse transformation $s^{-1}(\mathbf{x})$ can be applied 
to obtain the original image.

% A logarithmic scaling was used originally, but this did not provide good results with the GAN architecture that used 
% the hyperbolic tangent ($\tanh$) activation because the logarithm of a negative number is undefined. The models using 
% $\tanh$ activations achieved much better results than models without these activations.

@@

The ACGAN implementation was limited by the GPU memory capacity - the parameters and architectures together with the 
sample batch sizes meant that the GPU was easily saturated. Deeper models with more convolutional units were implemented 
but these tended to stall the GPU. A training loop for $10^5$ epochs for the $200 \: h^{-1} \: \textup{Mpc}$ cubes 
formatted to $32 \times 32 \times 32$ pixel histograms took approximately 144 hours on an NVIDIA Tesla V100 GPU with 
32GB capacity. To augment the dataset with additional diversity for each redshift, the samples were rotated in-situ during training as the sample batches were gathered.

@@

where a discrete set of points between points $q_1$ and $q_2$ are passed to the generator model to create samples~with and
$\mu$ are the discrete proportioned steps between $q_1$ and $q_2$. It should be noted that simple linear interpolation 
along a given axis of the latent space would disregard the curvature of the 256-dimensional latent space and so the path 
along a great circle by spherical interpolation is required.

% In these cases, we have performed a linear interpolation which assumes that the latent space is uniformly distributed 
% hypercube. Technically, our chosen latent space is a 100-dimension hypersphere or multimodal Gaussian distribution.

@@

\section{Statistics and diagnostics}\label{methods:stats_and_diags}
% WHAT ARE THESE MEASURES FOR? WHY ARE THEY IMPORTANT TO THE EXPERIMENT ? 
% WHAT DO THE STATS CONSIST OF IN MAKING? WHAT DO THEY SHOW?

@@

% \begin{figure}[!ht]%[hbt!]
% \includegraphics[width=\columnwidth]{figures/diagrams/kernel_fig.png}
% \centering
% \caption{A histogram down-sampled with three kernels of size $k=\{1, 2, 4\}$ (from left to right).}
% \label{fig:kernel_fig}
% \end{figure}

@@

\subsection{Generated images}
% show generated images at various redshifts, compare with training data
Figures~\ref{fig:t_z_imgs} and ~\ref{fig:g_z_imgs} show separate collections of simulated cosmic web and GAN-generated 
cosmic web for each class of redshift in the Millennium-SAGE training data. Across each value of redshift the ACGAN 
demonstrates its ability to evaluate each point in the latent space to a strong representation of a sample at the equivalent
redshift drawn from the model distribution. The ACGAN replicates the pixel density statistics well but the main downfall is 
in the reproduction of filament structure in the generated images. Typically the generated filaments are not as thin as their 
real counterparts in the training data.

Across the generated samples there is no evidence of generator mode collapse whereby a small set of characteristics are 
reproduced across the generated samples. They show as much mutual difference as the training images.

@@

\begin{figure*}[hbt!]
\includegraphics[width=17cm]{figures/cubes/acgan3d_g_fig.png}
\centering
\caption{A collection of training data cubes extracted from the Millennium-SAGE catalogs.Each row corresponds to the 
         redshift value given above each cube. The scaling $s(\mathbf{x})$ is applied to each cube $\mathbf{x}$.}
\label{fig:g_z_imgs}
\end{figure*}

% \begin{figure*}[hbt!]
% \includegraphics[width=16cm]{figures/cubes/acgan2d_t_fig.png}
% \centering
% \caption{A collection of 2D-projections of training data cubes extracted from the Millennium-SAGE catalogs. Each row 
%          corresponds to the redshift value given above each cube. The scaling $s(\mathbf{x})$ is applied to each cube 
%          $\mathbf{x}$.}
% \label{fig:t_z_imgs_2d}
% \end{figure*}

% \begin{figure*}[hbt!]
% \includegraphics[width=17cm]{figures/cubes/acgan2d_g_fig.png}
% \centering
% \caption{A collection of 2D-projections of generated data cubes extracted from the Millennium-SAGE catalogs. Each row 
%          corresponds to the redshift value given above each cube. The scaling $s(\mathbf{x})$ is applied to each cube 
%          $\mathbf{x}$.}
% \label{fig:t_z_imgs_2d}
% \end{figure*}

@@

Figure~\ref{fig:acgan_interp} shows the results of varying the class label for a single latent-space point. Between the 
minimum and maximum redshifts $z=0.0$ and $z=5.0$ respectively, 40 class examples were generated.

\begin{figure}[!ht]%[hbt!]
\includegraphics[width=\columnwidth]{figures/cubes/acgan3d_interp.png}
\centering
\caption{A collection of images generated with an array of redshift values for a single latent-space point.}
\label{fig:acgan_interp}
\end{figure}

@@

\subsubsection{Latent space point interpolation}

\subsubsection{Unseen redshift testing}
To test the power of the ACGAN generative approach, a selection of redshift values were selected from the Millennium-SAGE
snapshots to obtain new and unseen redshift data. This unseen data was used to register the ability of the generator to
create cubes at a redshift to which the discriminator had never been shown in training.

The new redshifts are $z'=\{0.51, 1.50, 2.62, 3.58, 4.52\}$ where the original redshift values $z$ shown to the
ACGAN are $z=\{0.0, 1.07, 2.07, 3.06, 4.17, 5.28\}$. With these new redshifts the same $D_{KL}$-trials were repeated and 
the results are shown in 
% plot unseen z cubes against true redshifts: 5 rows, 6 cols: 3 real, 3 gen

@@

\begin{figure}[!ht]%[hbt!]
\includegraphics[width=\columnwidth]{figures/graphs/metrics.png}
\centering
\caption{The loss and accuracy curves for the training of the ACGAN.}
\label{fig:acgan_losscurve}
\end{figure}

@@

\subsubsection{Training redshift trials}

Figure~\ref{fig:kl_trials_all} and Table~\ref{tab:1} show the results of the $D_{KL}$-trials for batches of 32 samples from 
each distribution repeated for 64 separate comparisons between each distribution pairing. The procedure for the repeated 
ensemble KL divergence testing outlined in Section~\ref{methods:stats_and_diags} used the samples transformed into 
probability distributions over the pixel density.

There is a slight broadening of the histograms with increasing kernel size. This shows the random effect, or dispersion, 
on the $D_{KL}$ value from repeated tests to on separate ensembles of histograms. This is caused by the loss of information 
due to the down-sampling of larger areas causing more variance in a given value of pixel density because of the averaging 
over the original pixels. This is predicted by the central-limit theorem. In this discussion a `mutual comparison' 
refers to the KL divergence $D_{KL}$ between two different ensembles from the same distribution of $t$, $g$ or $u$. The 
mutual $D_{KL}$ comparisons that show the most broadening are the mutual comparisons which together have increasing 
variance and separation with kernel size. This shows that in both cases the distributions are composed very differently 
to the uniform distributions. The means of the mutual distributions stay the same except for the uniform-uniform comparison. 
This is because the median for the bin separations in the component-histograms was given by the median of the training data 
batch which consistently has a lower mean pixel density than the uniform histogram data.

\begin{figure*}[hbt!]
\includegraphics[width=17cm]{figures/graphs/kl_trials_all_z_train.png}
\centering
\caption{Histograms showing the $D_{KL}$ values for distribution-comparisons between training $t$, generated $g$ and 
         uniform $u$ cube samples. This graph shows the results for downsampling kernel values $k \in \{1, 2, 4\}$.}
\label{fig:kl_trials_all}
\end{figure*}

The similar values of the generated-generated $D_{KL}$ average comparison with the training-training average shows the 
ability of the generator to represent multiple modes in the latent space with as much variety as the simulation data. 
This was affirmed by the training not displaying any mode collapse after converging. The narrower widths of the $t||g$ 
and $g||t$ comparisons stems from the generator creating a subset of images drawn from the data distribution. This could
well be a limitation from the capacity of the model.

The separate kernels cause averaging over different sized volumes. By construction the histograms are already sampling a 
volume at a fixed resolution for every distribution and so the kernel sizes give the same volume at different levels of 
resolution. A histogram from any distribution with each kernel down-sampling will exhibit different scales of structure 
from the original unsampled histogram and this is shown in Figure~\ref{fig:kernel_fig}. The ensembles drawn from each 
distribution are necessary to measure the difference in the structure from the distributions that is not inherent in the 
individual variance of the images themselves. The latter difference does not concern the distributions of the samples and 
is less important for the test of the generator capability. The disparity in the $D_{KL}$ means for each kernel dictates 
how the structure correlates on each scale. The matching alignment of the means along the $t||g$ and $t||t$ columns for 
all values of $k$ provides more evidence for the ability of the generator model. In opposition to this the $t||u$ and $g||u$
columns show $D_{KL}$ means that increase with $k$ and whose separations (between KL comparison means $D_{KL}(a||b)$ and
$D_{KL}(b||a)$) increase.

The widths of the mutual comparison histograms in the $D_{KL}$ trials show that there is an inherent difference in the 
information content of the ensembles from distributions. Some contribution to this is from the difference in the information
content of the batches themselves. Within the fixed specifications of the histograms it would be expected that the mutual 
comparisons show very close values.

An important characteristic of the training-generated comparisons is that the $D_{KL}$-histograms of these distribution 
pairs overlap. This gives evidence that the distributions can effectively represent each other. The mean $D_{KL}(t||g)$ and 
$D_{KL}(g||t)$ values are all nearly a whole order of magnitude smaller than the training-uniform and generated-uniform 
comparison means. These values of the training-uniform and generated-uniform together show that the generator 
representations are close to the training data because of their similarity in the mean, variance and mean-separations 
for all values of $k$. This shows the generator is able to create samples that are strongly correlated to the training 
data samples, to an extent that is independent of redshift $z$. % check again

The $D_{KL}$ values of the training-generated comparisons are lower by nearly a whole order of magnitude than the 
training-uniform and generated-uniform comparisons for all kernel sizes. This is the most important result of this report 
because it is evidence for the generator being able to generate samples that are statistically similar to the training data
samples. These values show that much less information would be lost if the model distribution was used in place of the data 
distribution as opposed to the uniform distribution, and that the amount lost is around a factor of two more than that of the 
training distribution approximating itself with different ensembles. This is supported by the horizontal separations of the 
histogram peaks in each column of the first three columns of Figure~\ref{fig:kl_trials_all}. The values of the $D_{KL}(t||g)$ 
and $D_{KL}(g||t)$ are nearly the same as the $D_{KL}(t_1||t_2)$ and $D_{KL}(t_2||t_1)$ values which suggests that replacing 
the $p_{data}$ distribution with the $p_{model}$ distribution would provide realistic samples for the same potential uses 
of the training data. This is because the $D_{KL}(t||t)$ and $D_{KL}(t||t)$ values are nearly the same as the $D_{KL}(t||g)$
and $D_{KL}(g||t)$ values as well as the fact that they are both smaller than the uniform-generated and uniform-training 
comparisons. % check 
The mutual $D_{KL}$ comparisons of the training and generated samples show agreement across the different kernels $k$ and
redshifts $z$. This shows the generators ability to reproduce a variety of structure in the training data samples at a variety 
of redshifts. 
% except for a difference of $10^{-3}$ in the variance of the $k=4$ comparison. 
% The higher $D_{KL}$ average in the $k=1$ training-generated comparisons are expected; the $D_{KL}$ statistic has more individual pieces of information to compare and find differences with. % check exact figures / statements

The $k=4$ kernel, whilst being the largest kernel, does not completely measure the continuity of filament structures over 
a number of the pixels in the $k=4$ down-sampled histograms. This could be tested with a few larger kernel-sizes in histograms 
with a greater number of total pixels. This could also be measured using a cosmological test such as the two-point correlation 
function or power spectrum. An increase in the number of bins for the component-histograms would measure the similarity of
the generator images to the training data images better. The values of the standard deviation of each $D_{KL}$ histogram 
relative to the values of the means suggests the number of trials sufficiently sampled the true $D_{KL}$ mean in each test.
% The empty plot of Figure~\ref{fig:kl_trials_all} appears this way because the density bin boundary is lower than the median 
% and mean of the uniform distribution over the pixel densities. The $D_{KL}$ value for this comparison is much lower than $10^{-2}$.

The differences between the training-uniform and generated-uniform means and variances show the significance of the 
training-generated comparisons. The mean $D_{KL}$ values of the training-generated comparisons are almost at the value of 
the training-training comparison means which is more evidence for the understandings of the training data by the generator. 
The similarity shown by the $D_{KL}(t||g)$ and $D_{KL}(g||t)$ values may mostly be due to the similar pixel density 
distributions of the training and generated data. Considering that the lack of filament structure in the larger scales 
of the generated data compared to the training data is not shown in the $D_{KL}$ comparisons, this may be true.

The pixel density distribution is an important characteristic of the images but the just obtaining the 
similarity between the $t$ and $g$ distributions with this property would not guarantee that all the structure in the 
training data was present. There are many combinations of pixels that make up a matching pixel-density distribution for 
two histogram distributions, but far less of those show the structure of the cosmic web. 
% The higher standard deviations in the $D_{KL}$ histograms for the 2D case in all the kernel sizes compared to the 3D cases is due to the larger size of features relative to total size of the image that shows them in either case.

@@

\begin{table*}[t]
  \centering
  \begin{tabular}{|ccccccc|}
    \hline\hline
          & $\langle D_{KL}(t||g) \rangle_z$ & $\langle D_{KL}(t||u) \rangle_z$ & $\langle D_{KL}(g||u)\rangle_z$ & $\langle D_{KL}(t||t)\rangle_z$ & $\langle D_{KL}(g||g) \rangle_z$ & $\langle D_{KL}(u||u) \rangle_z$ \\ 
          &  $\langle D_{KL}(g||t)\rangle_z$ & $\langle D_{KL}(u||t)\rangle_z$ & $\langle D_{KL}(u||g)\rangle_z$ & $\langle D_{KL}(t||t) \rangle_z$ & $\langle D_{KL}(g||g)\rangle_z$  & $\langle D_{KL}(u||u)\rangle_z$ \\ [1.0ex]
    \hline\hline

    $k=1$ & $0.060\pm0.005$ & $0.103\pm0.006$ & $0.134\pm0.007$ & $0.032\pm0.006$ & $0.033\pm0.006$ & $0.034\pm0.006$ \\
          & $0.057\pm0.004$ & $0.088\pm0.005$ & $0.120\pm0.006$ & $0.032\pm0.006$ & $0.033\pm0.006$ & $0.034\pm0.006$ \\ [1ex]

    $k=2$ & $0.054\pm0.006$ & $2.313\pm0.084$ & $2.317\pm0.165$ & $0.033\pm0.006$ & $0.034\pm0.007$ & $0.059\pm0.016$ \\
          & $0.052\pm0.005$ & $0.253\pm0.009$ & $0.271\pm0.017$ & $0.033\pm0.006$ & $0.034\pm0.007$ & $0.062\pm0.017$ \\ [1ex]

    $k=4$ & $0.051\pm0.008$ & $6.448\pm0.131$ & $6.492\pm0.418$ & $0.033\pm0.007$ & $0.033\pm0.007$ & $0.030\pm0.009$ \\
          & $0.049\pm0.006$ & $0.386\pm0.015$ & $0.406\pm0.033$ & $0.033\pm0.007$ & $0.033\pm0.007$ & $0.030\pm0.009$ \\ [1ex]

    \hline\hline
  \end{tabular}
  \caption{Results from the $D_{KL}$ trials between each distribution averaged over redshift $z$ for each kernel size $k$.}
  \label{tab:1}
\end{table*}

\subsubsection{Unseen redshift trials}

Figure~\ref{fig:kl_trials_all_z2} and Table~\ref{tab:2} show the results of the $D_{KL}$-trials between for batches of 32 
samples from each distribution repeated for 64 separate comparisons between each distribution pairing. These results are 
produced by using the generator to create samples at values of redshift $z=z'$ that the ACGAN has never been exposed to.

\begin{figure*}[hbt!]
\includegraphics[width=17cm]{figures/graphs/kl_trials_all_z_unseen.png}
\centering
\caption{Histograms showing the $D_{KL}$ values for distribution-comparisons between training $t$, generated $g$ and 
         uniform $u$ cube samples with cube samples from unseen redshift snapshots in the Millennium-SAGE simulation 
         data This graph shows the results for downsampling kernel values $k \in \{1, 2, 4\}$.}
\label{fig:kl_trials_all_z2}
\end{figure*}

\begin{table*}[t]
  \centering
  \begin{tabular}{|ccccccc|}
    \hline\hline
          & $\langle D_{KL}(t||g) \rangle_{z'}$ & $\langle D_{KL}(t||u) \rangle_{z'}$ & $\langle D_{KL}(g||u)\rangle_{z'}$ & $\langle D_{KL}(t||t)\rangle_{z'}$ & $\langle D_{KL}(g||g) \rangle_{z'}$ & $\langle D_{KL}(u||u) \rangle_{z'}$ \\ 
          &  $\langle D_{KL}(g||t)\rangle_{z'}$ & $\langle D_{KL}(u||t)\rangle_{z'}$ & $\langle D_{KL}(u||g)\rangle_{z'}$ & $\langle D_{KL}(t||t) \rangle_{z'}$ & $\langle D_{KL}(g||g)\rangle_{z'}$  & $\langle D_{KL}(u||u)\rangle_{z'}$ \\ [1.0ex]
    \hline\hline

    $k=1$ & $0.146\pm0.010$ & $0.100\pm0.005$ & $0.073\pm0.005$ & $0.069\pm0.004$ & $0.081\pm0.004$ & $0.109\pm0.007$ \\
          & $0.033\pm0.006$ & $0.033\pm0.006$ & $0.036\pm0.007$ & $0.036\pm0.007$ & $0.033\pm0.006$ & $0.033\pm0.006$ \\
          [1ex]

    $k=2$ & $0.650\pm0.045$ & $0.166\pm0.007$ & $1.390\pm0.074$ & $0.208\pm0.009$ & $0.343\pm0.021$ & $0.174\pm0.011$ \\
          & $0.033\pm0.006$ & $0.033\pm0.006$ & $0.059\pm0.013$ & $0.061\pm0.014$ & $0.067\pm0.014$ & $0.067\pm0.014$ \\
          [1ex]

    $k=4$ & $2.233\pm0.120$ & $0.253\pm0.011$ & $5.658\pm0.358$ & $0.417\pm0.022$ & $2.986\pm0.249$ & $0.353\pm0.025$ \\
          & $0.033\pm0.008$ & $0.032\pm0.008$ & $0.061\pm0.018$ & $0.062\pm0.017$ & $0.080\pm0.025$ & $0.080\pm0.025$ \\
          [1ex]
    \hline\hline
  \end{tabular}
  \caption{Results from the $D_{KL}$ trials between each distribution averaged over values of unseen redshift $z'$ for each 
           kernel size $k$.}
  \label{tab:2}
\end{table*}

The results point to the fact that the generator is less competent at representing values of redshift that lay between the
values that the ACGAN has been exposed to in training. This is certainly to be expected as the description for the emergence
of the finite training set of images is certainly more simple than the chronology of the cosmic web that the Millenium-SAGE
models characterise. Figure~\ref{fig:z_kl} shows the relation between the $\langle D_{KL}(g||t) \rangle$ and 
$\langle D_{KL}(t||g) \rangle$ values with redshift $z$. The highest peak coincides with the lowest unseen redshift $z'=0.51$.

% lack of data? lack of feature maps

\begin{figure}[!ht]%[hbt!]
\includegraphics[width=\columnwidth]{figures/graphs/z_kl.png}
\centering
\caption{The KL-trial means $\langle D_{KL} \rangle$ for comparisons of image distributions 
         $t$ and $g$ for all redshifts $z$ and $z'$ }
\label{fig:z_kl}
\end{figure}
